### 2022-11-13 NSF2022/Description/backgroundv3.tex
new domain figure

\begin{figure}
  \begin{center}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/3Particles.jpg}
    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/Domain.jpg}
    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/3Particles.jpg}
  \end{center}
  \caption{\label{fig:flow_map} \footnotesize {\em Left:} In the HAP
  formulation~\cite{Fu2018_SIAM}, a system of exterior problems defines
  the hydrodynamic and hydrophobic interactions. {\em Right:} Particles
  translate and rotate to lower the free energy $E[u]$ subject
  to~\eqref{eqn:phase}, $W(\phi) = \phi^2$, and reach a minimal
  configuration in panel C. The colormap is blue for $\eta = 0$ and red
  for $eta = 1$. The arrows are the velocity field $\uu$.}
\end{figure}

@@

\begin{wrapfigure}[21]{r}{3.2in}
  \vspace{-10pt}
  \begin{center}
    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize \label{fig:self-assembly2} Changes in the
  boundary condition \eqref{eqn:material} yield distinct morphologies.
  Each row has the same initial configuration, $W(\phi) =
  \tfrac{1}{2}\phi^2$. (\emph{Top}) Granules with an amphiphilic
  boundary condition results in a bilayer pattern (yellow, $\phi = 1$,
  blue, $\phi = 0$). (\emph{Middle}) Granules with $\phi = 2$ (magenta)
  on one side and $\phi = 1$ on the other form multilamellar bilayers.
  (\emph{Bottom}) Bipolar granules with $\phi = 1$ (yellow) on one side
  and $\phi=-1$ (green) on the other side form a checkerboard pattern.}
\end{wrapfigure}

@@

\subsection{Applications}
Since the framework is scale independent, it can be applied to a broad range
of nonspecific self-organization phenomena in surface chemistry, biology
and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly. For example,
three bodies with amphiphilic label (\S\ref{sec:specificaim1})
spontaneously self-organize to sequester the hydrophobic fluid phase
(Figure~\ref{fig:flow_map}). Changes in the boundary conditions result
in distint morphologies (Figure~\ref{fig:self-assembly2}) whose rheology
can be further investigate (\S\ref{sec:specificaim3}).
%
A concrete application the PIs have considered in their
SIAM Multiscale Modeling and Simulation and Journal of Fluid Mechanics works
\cite{Fu2018_SIAM, FuQuRyYo22}
is the problem of \emph{vesicle hydrodynamics}.
A vesicle is a small, fluid filled membrane sack.
The goal in vesicle hydrodynamics is to study the flow patterns 
that arrise due to the interaction
between membrane elasticity and the fluid.

A striking aspect of our hydrodynamic
simulation is its fidelity to physics.
The model contains a few
parameters; granule radius $c$,
screening length $\epsilon$,
surface tension $\gamma$.
When set to realistic values in the literature
\cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian, Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016},
we quantitatively recover many of the well-known
elastic moduli for single-component lipid bilayers
\cite{Nagle17, Nagle17-2, LeVeWa14,NAGLE2000159}. 
Such agreement is a validation that equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} 
correctly capture the long-range interactions between amphiphilic granules (such as lipid macromolecules) surfaces.

\begin{wrapfigure}[9]{l}{0.46\textwidth}
\vspace{-10pt}
\includegraphics[width=0.46\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
\vspace{-20pt}
\caption{\label{fig:JPv_linearshear} \footnotesize Granular vesicles
  undergo tank-treading in background shear flow.}
\end{wrapfigure}
%
In terms of hydrodynamics, the granule vesicles in background flows
replicate the behaviour of an continous, inextensible, elastic vesicle
with permeability. The simulations showed, for the first time, a
granule-vesicle suspension behaving as a tank-treading vesicle
\cite{Finken2008, Shaqfeh11} (see Figure \ref{fig:JPv_linearshear}).
Movies of Figure \ref{fig:JPv_linearshear} reveal intermonolayer slip
and derived values for intermonolayer friction were in good quantitative
agreement those derived by atomistic and Martini force field simulation
studies \cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}. In
Figure \ref{fig:JPv_rupture}, membrane rupture occurs at large shear
rates and yields a dimensional scaling for critical rupture shear rate
\cite{VLAHOVSKA2009775,keller_skalak_1982}. A side-by-side comparison of
granule-based vesicles and the sharp interface representation yielded
shapes and trajectories that overlapped.

\begin{wrapfigure}[14]{r}{0.475\textwidth}
%\vspace{-10pt}
\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
\caption{\label{fig:JPv_rupture} \footnotesize Rupture of a granular
  vesicle under large shear rates.}
\end{wrapfigure}

%Having a non-specific model that replicates physical details
%is the crown jewel of applied mathematics.
The mathematical framework in equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance}
are highly desirable from the applied math point of view as there are many
\emph{Further Applications}, such as
(i) amphiphilic Janus spheres that form diverse suprastructures
\cite{HaBr20,McBr21,Bradley2017},
(ii) pickering emulsions involving
two-phase fluids and dense suspensions \cite{Bradley2016},
(iii) creation and manipulation of small droplets
using amphiphilic microparticles \cite{Ha2022SurfaceEM,Ha2020MinimalSC},
and (iv) tension drivent fabrication of microstructures
~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.
\begin{wrapfigure}[9]{l}{2.1in}
  \vspace{-5pt}
  \centering
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em right}) requires meshing only the
  boundary of the domain.}
\end{wrapfigure}

\subsection{Computational method and mathematical properties}
Computational methods to solve the PDEs~\eqref{eqn:stokes}
and~\eqref{eqn:phase} are challenging to develop because of
the complicated and unbounded domain.
This challenge is compounded when dense
suspensions are considered. Integral equations (IEs) offer an
alternative formulation of the PDEs that only require meshing the
boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}), and the automatically satisfy far field
conditions. Additional advantages of an discretizations of IE
formulations include high-order, or even spectral, accuracy and
well-conditioned linear system that can be solved iteratively with a
mesh-independent number of Krylov iterations such as the generalized
minimal residual method (GMRES). However, IEs have challenges: nearly
touching granules requires a quadrature rule for nearly-singular
integrals; their discretization results in dense matrices; and they
cannot immediately be applied to non-linear PDEs. The IE community,
including PI Quaife, has developed a variety of tools to address these
numerical challenges, and we discuss in \S~\ref{sec:specificaim2}.

In the absence of external flow, the
system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
\begin{align}
\label{eq:energy_law}
  \begin{split}
  \frac{d}{dt}E
    &= - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx, \\
    E &= \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
  \end{split}
\end{align}
%\begin{align}
%\label{eq:energy_law}
%  \frac{d}{dt}E
%  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
%  \uu^T|^2 \,d\xx,\quad
%    E = \gamma \int_{\Omega(t)}
%  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
%\end{align}
Here $E$ is the energy stored in the phase transitions
and the energy law states that
the granules move to decrease energy,
which is lost due to viscous dissipation.
The derivation of \eqref{eq:energy_law} is interesting
because $E$ depends both on $\phi$
and $\Omega(t)$. It uses the Rayleigh Transport Theorem to write the time
derivative of $E$ as an energy density flux through the boundary
involving the phase stress $T_i$, and a bulk term involving the Euler-Lagrange
derivative of $E$~\cite{Fu2018_SIAM}. The Euler-Lagrange derivative vanishes due
to~\eqref{eqn:phase} and the boundary flux transforms into viscous
dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations. Figure~\ref{fig:coarsening} summarizes the general evolution of $E$ from the self-assembly process to
the collective dynamics of the assembly under external forcing.
\begin{wrapfigure}[16]{r}{4in} 
  \includegraphics[width=4in]{figures/Background/coarsening.pdf}
  \vspace{-20pt}
  \caption{\label{fig:coarsening} \footnotesize Energy $E$ in
  equation~(\ref{eq:energy_law}) of a suspension of amphiphilic granules
  versus time $t$. Under the moving domain problem
  \eqref{eq:RBT}--\eqref{eqn:hydro_stress} with amphiphilic boundary
  condition, the granules self-organize into vesicle bilayers. External
  hydrodynamic effects are introduced to study elastic properties of
  the granules assembly~\cite{Fu2018_SIAM,FuQuRyYo22}.}
  \vspace{5pt}
\end{wrapfigure}

>>>>

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{figures/Background/Domain.pdf}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/3Particles.jpg}
%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/3Particles.jpg}
  \end{center}
  \caption{\label{fig:flow_map} \footnotesize
  (a) Granules make a superstructure e.g., a vesicle. The panel shows
  the moving domain $\Omega(t)$, granules with centers $\aa_i$ and directors $\dd_i$,
  and the unit inward normal $\nu.$ Panels b, c, d show the
  interplay between the phase field $\phi$ (colormap) and granule configuration.
  Red is for $\phi = 1$ and blue for $\phi = 0$; $W(\phi) = \tfrac{1}{2}\phi^2$.
  The white arrows are the fluid velocity field.  
  }
\end{figure}

@@

\begin{wrapfigure}[21]{r}{3.2in}
  \vspace{-15pt}
  \begin{center}
    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize \label{fig:self-assembly2} Changes in the
  boundary condition \eqref{eqn:material} yield distinct morphologies.
  Each row has the same initial configuration, $W(\phi) =
  \tfrac{1}{2}\phi^2$. (\emph{Top}) Granules with an amphiphilic
  boundary condition results in a bilayer pattern (yellow, $\phi = 1$,
  blue, $\phi = 0$). (\emph{Middle}) Granules with $\phi = 2$ (magenta)
  on one side and $\phi = 1$ on the other form multilamellar bilayers.
  (\emph{Bottom}) Bipolar granules with $\phi = 1$ (yellow) on one side
  and $\phi=-1$ (green) on the other side form a checkerboard pattern.}
\end{wrapfigure}

@@

\subsection{Applications}
Since the framework is scale independent, it can be applied to a broad range
of nonspecific self-organization phenomena in surface chemistry, biology
and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly. For example,
three bodies with amphiphilic label (\S\ref{sec:specificaim1})
spontaneously self-organize to sequester the hydrophobic fluid phase
(Figure~\ref{fig:flow_map}). Changes in the boundary conditions result
in distint morphologies (Figure~\ref{fig:self-assembly2}) whose rheology
can be further investigate (\S\ref{sec:specificaim3}).
%
A concrete application the PIs have considered in their
SIAM Multiscale Modeling and Simulation and Journal of Fluid Mechanics works
\cite{Fu2018_SIAM, FuQuRyYo22}
is the problem of \emph{vesicle hydrodynamics}.
A vesicle is a small, fluid filled membrane sack.
The goal in vesicle hydrodynamics is to study flow patterns 
arrising from the interaction
between membrane elasticity and the fluid.

\begin{wrapfigure}[11]{l}{0.48\textwidth}
\vspace{-5pt}
\includegraphics[width=0.48\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
\vspace{-20pt}
\caption{\label{fig:JPv_linearshear} \footnotesize Granular vesicles
  undergo tank-treading in background shear flow.}
\end{wrapfigure}
%
A striking feature of our hydrodynamic
simulations is their fidelity to physics.
The model contains a few
parameters; granule radius $c$,
screening length $\epsilon$,
surface tension $\gamma$.
When set to their realistic values 
\cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian, Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016},
we quantitatively recover many of the well-known
elastic moduli for single-component lipid bilayers
\cite{Nagle17, Nagle17-2, LeVeWa14,NAGLE2000159}. 
Such agreement is a validation that equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} 
correctly capture the long-range interactions between amphiphilic granules (such as lipid macromolecules) surfaces.
\newpage

\begin{wrapfigure}[13]{l}{0.475\textwidth}
\vspace{-10pt}
\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
\caption{\label{fig:JPv_rupture} \footnotesize Rupture of a granular
  vesicle under large shear rates.}
\end{wrapfigure}
In terms of hydrodynamics, the granule vesicles in background flows
replicate the behaviour of an continous, inextensible, elastic vesicle
with permeability. The simulations showed, for the first time, a
granule-vesicle suspension behaving as a tank-treading vesicle
\cite{Finken2008, Shaqfeh11} (see Figure \ref{fig:JPv_linearshear}).
Movies of Figure \ref{fig:JPv_linearshear} reveal intermonolayer slip
and derived values for intermonolayer friction were in good quantitative
agreement those derived by atomistic and Martini force field simulation
studies \cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}. In
Figure \ref{fig:JPv_rupture}, membrane rupture occurs at large shear
rates and yields a dimensional scaling for critical rupture shear rate
\cite{VLAHOVSKA2009775,keller_skalak_1982}. A side-by-side comparison of
granule-based vesicles and the sharp interface representation yielded
shapes and trajectories that overlapped.

%Having a non-specific model that replicates physical details
%is the crown jewel of applied mathematics.
The mathematical framework in equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance}
is highly desirable from the applied math point of view as there are many
\emph{Further Applications}, such as
(i) amphiphilic Janus spheres that form diverse suprastructures
\cite{HaBr20,McBr21,Bradley2017},
(ii) pickering emulsions involving
two-phase fluids and dense suspensions \cite{Bradley2016},
(iii) creation and manipulation of small droplets
using amphiphilic microparticles \cite{Ha2022SurfaceEM,Ha2020MinimalSC},
and (iv) tension drivent fabrication of microstructures
~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.

\subsection{Computational method and mathematical properties}
\begin{wrapfigure}[15]{r}{2.1in}
  \vspace{-0pt}
  \centering
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}\\
  \includegraphics[width=2in]{figures/Background/NSF.pdf}\\
\caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em top left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em top right}) requires meshing only the
  boundary of the domain.
  ({\em bottom}) BIE can handle intricately shaped domains as well.}
\end{wrapfigure}
Computational methods to solve the PDEs~\eqref{eqn:stokes}
and~\eqref{eqn:phase} are challenging to develop because of
the complicated and unbounded domain.
This challenge is compounded when dense
suspensions are considered. Integral equations (IEs) offer an
alternative formulation of the PDEs that only require meshing the
boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}), and the automatically satisfy far field
conditions. Additional advantages of an discretizations of IE
formulations include high-order, or even spectral, accuracy and
well-conditioned linear system that can be solved iteratively with a
mesh-independent number of Krylov iterations such as the generalized
minimal residual method (GMRES). However, IEs have challenges: nearly
touching granules requires a quadrature rule for nearly-singular
integrals; their discretization results in dense matrices; and they
cannot immediately be applied to non-linear PDEs.
\S~\ref{sec:specificaim2} discusses
a variety of tools the IE community,
including PI Quaife, has developed
to address these numerical challenges.

In the absence of external flow, the
system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
%\begin{align}
%\label{eq:energy_law}
%  \begin{split}
%  \frac{d}{dt}E
%    &= - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
%  \uu^T|^2 \,d\xx, \\
%    E &= \gamma \int_{\Omega(t)}
%  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
%  \end{split}
%\end{align}
\begin{align}
\label{eq:energy_law}
  \frac{d}{dt}E
  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx,\quad
    E = \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
\end{align}
Here $E$ is the energy stored in the phase transitions
and the energy law states that
the granules move to decrease energy,
which is lost due to viscous dissipation.
The derivation of \eqref{eq:energy_law} is interesting
because $E$ depends both on $\phi$
and $\Omega(t)$. It uses the Rayleigh Transport Theorem to write the time
derivative of $E$ as an energy density flux through the boundary
involving the phase stress $T_i$, and a bulk term involving the Euler-Lagrange
derivative of $E$~\cite{Fu2018_SIAM}. The Euler-Lagrange derivative vanishes due
to~\eqref{eqn:phase} and the boundary flux transforms into viscous
dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations. Figure~\ref{fig:coarsening} summarizes the general evolution of $E$ from the self-assembly process to
the collective dynamics of the assembly under external forcing.
\begin{wrapfigure}[16]{r}{4in} 
  \includegraphics[width=4in]{figures/Background/coarsening.pdf}
  \vspace{-20pt}
  \caption{\label{fig:coarsening} \footnotesize Energy $E$ in
  equation~(\ref{eq:energy_law}) of a suspension of amphiphilic granules
  versus time $t$. Under the moving domain problem
  \eqref{eq:RBT}--\eqref{eqn:hydro_stress} with amphiphilic boundary
  condition, the granules self-organize into vesicle bilayers. External
  hydrodynamic effects are introduced to study elastic properties of
  the granules assembly~\cite{Fu2018_SIAM,FuQuRyYo22}.}
  \vspace{5pt}
\end{wrapfigure}
